
\documentclass[12pt, letterpaper]{article}
\usepackage{graphicx}
\usepackage[margin=0.5in]{geometry}

\begin{document}
    \begin{center}
    \textbf{Sami Chamali - (+49) 17674652813 - sami.what@hotmail.com}


    \end{center}
\section{About Me}

I’m Sami Chamali, a passionate Computer Enthusiast! I love to occupy my time with developing and collaborating with AI companies and creating products and solutions for them! In my years of High School, I attended at least 2 competitions on average per year! Most of which I was offered internships and jobs by major companies… I am deeply interested in Software, Mechanical, and Computer Engineering, all of which I would love to include in my professional background!

\section{Education}
    \begin{itemize}
        \item \underline{Al Mawakeb School Al Garhoud}, 2011 - 2024, Dubai. \textbf{American High School Diploma}
        \item \underline{GISMA University of Applied Sciences}, 2024 - 2027, Berlin. \textbf{BEng. Software Engineering}
    \end{itemize}

\section{Work Experience}
    \begin{itemize}
        \item \textbf{Software Engineer} - \underline{LinguaGPT}. Liverpool, United Kingdom.
            \begin{enumerate}
                \item Developed Features that require \textbf{LLM Prompting}.
                \item Worked with \textbf{Internet Scraping} and \textbf{Information Extraction}.
                \item Built \textbf{algorithms} and \textbf{frameworks} to \underline{incase LLM's} and have them provide more detailed, and upto date information.
                \item Worked on \textbf{Databases} and how to \underline{manage User Information} and properly secure it using \textbf{modern tools}.
            \end{enumerate}
    \end{itemize}

\section{Languages Spoken}
    \begin{itemize}
        \item \textbf{Arabic} - Mother Language, Native.
        \item \textbf{English} - Fluent/Native.
            \begin{itemize}
                \item \textbf{Listening}: C2
                \item \textbf{Reading}: C1
                \item \textbf{Writing}: C1
                \item \textbf{Spoken Production}: C2
                \item \textbf{Spoken Interaction}: C2
            \end{itemize}
        \item \textbf{German} - Proficient.
        \begin{itemize}
            \item \textbf{Listening}: B2
            \item \textbf{Reading}: B1
            \item \textbf{Writing}: B2
            \item \textbf{Spoken Production}: B2
            \item \textbf{Spoken Interaction}: B2
        \end{itemize}
    \end{itemize}
\section{Projects}
    \begin{itemize}
        \item \textbf{Content Generator - Open Source Project.}
            A Content Generator that utilizes an LLM and internet scraping to dynamically generate well-structured documents of varying lengths, rich in information and traditionally partitioned.
    \end{itemize}
\end{document}
